Trip Summary ITHIM-R

### 2020-01-20 code/producing_trips_rd/trip-summary.Rmd
adding trip summary for cape town
updating repo

trip <- read_csv("../../data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

@@

>>>>

#trip <- read_csv("../../data/local/bogota/bogota_trip.csv")
#quality_check(trip)
#trip_summary$bogota_city <- value

@@

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv")
quality_check(trip)
trip_summary$cape_town <- value
